### 2013-09-17 intro.tex
second page with advisor / reader, fix page numbering

@@

The task of semantic segmentation is defined as predicting a semantic class label
for each pixel in a natural image. Predicting semantic labels on such a fine scale
provides ??? an important step towards general scene understanding.
%
Applications of scene understanding include automatic image interpretation for retrieval,
 autonomous driving and mobile robotics.
%
related work?? here again?
Current systems for semantic segmentation emply a wealth of different paradigms, most notably:
The ranking of figure ground hypotheses
conditional random field / superpixel? kraehenbuehl?
detector based
sparse coding

@@

Finally, Chapter~\ref{ch:nyu} applies the methods developed in Chapters~\ref{ch:structurd_pystruct} and \ref{ch:exact_learning}
to the problem of semantic annotation with structure classes in RGB-D data. We demonstrate that we are able to learn
meaningful spacial relations, and improve upon the state of the art in the NYU V2 datasets that we consider.

>>>>

\pagenumbering{arabic}

@@

The task of semantic segmentation is defined as predicting a semantic class label
for each pixel in a natural image. Predicting semantic labels on such a fine scale
constitutes an important step towards general scene understanding.
%
Applications of scene understanding include automatic image interpretation for retrieval,
 autonomous driving and mobile robotics.
%
related work?? here again?
Current systems for semantic segmentation emply a wealth of different paradigms, most notably:
The ranking of figure ground hypotheses
conditional random field / superpixel? kraehenbuehl?
detector based
sparse coding

@@

Finally, Chapter~\ref{ch:nyu} applies the methods developed in
Chapter~\ref{ch:structurd_pystruct} and Chapter~\ref{ch:exact_learning} to the
problem of semantic annotation with structure classes in RGB-D data. We
demonstrate that we are able to learn meaningful spacial relations, and improve
upon the state of the art in the NYU V2 datasets that we consider.
